% !TEX TS-program = xelatex
% !TEX encoding = UTF-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% INSTRUCTIONS FOR COMPILING THIS DOCUMENT ("CV.tex")
%% TEX ---(XeLaTeX)---> PDF:
%%
%% Method 1: Use latexmk for fully automated document generation:
%%   latexmk -xelatex "CV.tex"
%%   (add the -pvc switch to automatically recompile on changes)
%%
%% Method 2: Use XeLaTeX directly:
%%   xelatex "CV.tex"
%%   (run multiple times to resolve cross-references if needed)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper,10pt,oneside]{article}
%\documentclass[letterpaper,10pt,oneside]{article}

% Do not stop on errors during compilation.
\nonstopmode

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{CV-Preamble.tex}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\thispagestyle{empty}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\title{Benjamin Nicholes}

\begin{subtitle}
% {4555 40th Street Apt. 1R Sunnyside, New York 11104, USA}
\href{mailto:nicholes.ben@gmail.com}
{nicholes.ben@gmail.com}
\par
{New York, New York}
% \,\BulletSymbol\,
% +1\,(775)\,397-0089
\end{subtitle}

\begin{body}

%%%%%%%%%%%%%%%%%%%%%%%%%
%% WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Work Experience}
{Work Experience}
{PDF:WorkExperience}

{\textbf{Bombora}}
\par
Technical Product Analyst -- New York, NY
\hfill
\DatestampYM{2018}{01} -- Current
\begin{detail}
\BulletItem
Technical Product Analyst - Advertising Technology
\BulletItem
Conduct feasibility tests and engineer prototypes.
\BulletItem
Conduct regular customer interviews, and integrate feedback into products.
\BulletItem
Oversee and lead cross-functional teams across different offices and offshore development.
\BulletItem
Conduct market viability analysis, and create business plans for new product offerings.
\BulletItem
Lead development team for integrating Bombora Surge data into Facebook Custom Audiences.
\BulletItem
Lead development team for integrating Bombora Surge data into Marketo \newline and Oracle Eloqua Marketing Automation platforms.

\end{detail}

Junior DevOps Engineer -- New York, NY
\hfill
\DatestampYM{2017}{06} -- 
\DatestampYM{2017}{12}
\begin{detail}
\BulletItem
Manage and audit high availability SFTP environments for Bombora data assets.
\BulletItem
Develop, test and integrate Chef automation to new and existing Windows and Linux \newline infrastructure through Chef SDK, Ruby, Python, Powershell, and Bash.
\BulletItem
 Manage and Monitor Development and Production environments in AWS, Google Cloud, \newline and Microsoft AD through PRTG, Datadog, and New Relic.
\BulletItem On Call for degradation of Production environments.
 \BulletItem
 Create and manage CI pipelines with Jenkins.
\end{detail}
\par
DevOps Intern -- Reno, NV
\hfill
\DatestampYM{2016}{04} -- \DatestampYM{2017}{06} 
\begin{detail}
\end{detail}

\EntryGap

{\textbf{Ustyme}}
\par
Software Engineer Intern
\hfill
\DatestampYM{2015}{03} --
\DatestampYM{2016}{04}
\begin{detail}
\BulletItem
Implement features, test environment builds, document and solve bugs.
\BulletItem
Marketing/SEO: 
Develop and integrate best SEO practices for the marketing site \newline using Google Analytics and Google Dashboard.
\BulletItem
Create a custom mission control dashboard for business team detailing revenue,\newline daily users, etc. through Mixpanel API.
\BulletItem
Develop and Integrate Automated Test Cases in Javascript for the Ustyme App \newline through TestRail.
\BulletItem
Network/Cloud Administration:
Under mentorship develop and monitor Dev, \newline UAT, and Production environments through Github, AWS EC2, S3, VPC, Route 53,\newline Code Deploy, and Nginx.
\end{detail}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\section
{Education}
{Education}
{PDF:Education}

{\textbf{University Of Nevada Reno}},
Reno, Nevada
\par
Bachelor of Science (B.S.) in 
{Computer Science and Engineering}
\hfill
\DatestampY{2012} --
\DatestampY{2017}
\begin{detail}
\BulletItem
Cumulative GPA: 3.63 / 4.00
\BulletItem
Minor in 
{Mathematics}
\BulletItem
Minor in
{Business Administration}
\end{detail}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Projects %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Projects\newline}
{Projects}
{PDF:Projects}

\textbf{Eatrank.io}\par
EatRank allows users to rate their favorite dishes at restaurants.
\begin{detail}
\BulletItem
www.eatrank.io
\BulletItem
Co-Founder
\BulletItem
Find the best food in your city by rating and sharing dishes at restaurants.
\BulletItem
Engineered mobile first application.
\BulletItem
Created business plans and entered Business Competitions.
\end{detail}

% \EntryGap


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Community Service                      %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section
% {Community Service}
% {Community Service}
% {PDF:Community Service}

% {\textbf{Nevada Sagebrush Highschool Debate League}},
% Reno, NV
% \par
% Judge and Volunteer
% \hfill
% \DatestampY{2012} --
% {2015}\newline

% {\textbf{Code Reno}},
% Reno, NV
% \par
% Active Volunteer - Code Reno helps bring coding to kids in \newline workshops throughout the city.
% \hfill
% \DatestampY{2012}

%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\section
{Skills}
{Skills}
{PDF:Skills}

Linux Administration, Bash, Python, Javascript,
HTML, CSS, SQL, Git, Technical Writing, Business Plans, Product Management, Scrum, Agile, Kanban



%%%%%%%%%%%%
%% Technologies %%
%%%%%%%%%%%%

\section
{Technologies}
{Technologies}
{PDF:Technologies}

AWS,
GCP, Microsoft Server/AD, Jenkins, Marketo, Eloqua, Facebook Business Manager,
Google Big Query, New Relic, PRTG, Pagerduty, Nginx, Datadog, Chef, Datadog, Docker, Kubernetes, Microsoft Office Suite, Atlassian Suite

\end{body}

%%%%%%%%%%%
% CV NOTE %
%%%%%%%%%%%

\end{document}
